Multi-line Intensity Mapping

### 2019-04-27 paper/ms.tex
Update first fish mat eq

Eventually it will be desirable to place constraints on $\denps(k)$. For now,
however, we simply wish to understand how well future experiments will be able
to determine each of $B_i$ as a function of $z$. We can proceed simply by
computing the relevant Fisher matrix:
\beq\label{eq:fisher_tf}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where the sum of $l$, $l'$, $m$, and $m'$ is over each of the three lines.
Equation~\ref{eq:fisher_tf} can be readily modified to accomodate the case of
more than three lines (by extending the summations to include these lines) and
to accomodate the auto-spectra (by allowing $l=l'$ and $m=m'$ in the relevant
summations). We will consider these cases in Sections~\Gus{x}~and~\Gus{y},
respectively.

>>>>

Eventually it will be desirable to place constraints on $\denps(k)$. For now,
however, we simply wish to understand how well future experiments will be able
to determine each of $B_i$ as a function of $z$. We can proceed simply by
computing the relevant Fisher matrix:
\beq\label{eq:fisher_tf}
F_{i,j} = 
\int \frac{\text{d}^3k}{(2\pi)^3} V_{\text{surv}}
% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{l} \sum_{m}
\frac{\partial \hat{P}_{l}(\bm{k})}{\partial B_i}
\left(\Cov{\hat{P}_{l}(\bm{k})}{\hat{P}_{m}(\bm{k})}\right)^{-1}
\frac{\partial \hat{P}_{m}(\bm{k})}{\partial B_j}\text{,}
\eeq
where the sum over $l$ and $m$ each is over every \emph{pair} of lines.
Equation~\ref{eq:fisher_tf} can be readily modified to accomodate the case of
more than three lines (by extending the summations to include these lines) and
to accomodate the auto-spectra (by extending the sum over $l$ and $m$ to
include them). We will consider these cases in Sections~\Gus{x}~and~\Gus{y},
respectively.
